\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 photoz.tex
Added two sentences about the limitation of the Choi et al. analysis.
photoz.tex
Accepted HH's comment (but as a footnote)

In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.   The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample.  \citet{choi/etal:2016} found significant biases in the redshift distributions used in the original CFHTLenS analyses,
concluding that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.    This re-analysis was presented in \citet{joudaki/etal:2016} where the impact of correcting for the biases determined by \citet{choi/etal:2016}, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between constraints.  The best-fit model, however moved further from the Planck-preferred model, in agreement with the `toy-model' analysis of \citet{choi/etal:2016} which concluded that the effect of these biases would be to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 4$\%.

>>>>

In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.   The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample\footnote{The implication of a $z_B < 0.9$ high-redshift limit is that the analysis is unable to constrain the high-redshift tails of the redshift distributions due to the lack of high-$z$ spec-$z$ samples. As such the results from \citet{choi/etal:2016} are only the first important step towards a detailed understanding of the CFHTLenS tomographic redshift distributions and as such may be revised in the future.}.  \citet{choi/etal:2016} found significant biases in the redshift distributions used in the original CFHTLenS analyses,
concluding that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.    This re-analysis was presented in \citet{joudaki/etal:2016} where the impact of correcting for the biases determined by \citet{choi/etal:2016}, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between constraints.  The best-fit model, however moved further from the Planck-preferred model, in agreement with the `toy-model' analysis of \citet{choi/etal:2016} which concluded that the effect of these biases would be to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 4$\%.
